Red-Giant Hot Jupiters: Brilliant Radio Beacons? \memoTM{Since they are not that bright, maybe ``The Radio Emission from Red-Giant Hot Jupiters'' or ``A Novel Method for Detecting Red-Giant Hot Jupiters'' would be a better title?}

### 2015-09-10 ms.tex
Variability text/refs added

When stars less than $\sim$8~$M_\sun$ evolve off the main sequence, they evolve through the red-giant branch (RGB) and the asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude.
Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim 10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr. 
On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.

@@

\paragraph{Variability of stellar wind (months $\sim $)?}
Based on the correlation between the planetary radio emission and the solar wind plasma density also suggest that the radio emission from the planet around the evolved stars, which typically oscillate, are time variable.
\memoYF{To Jason: time variability?}
%
\paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
If the planetary orbit is close to the edge-on configuration, the radio emission disappears synchronously to the orbital period, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
The probability of the latter one, secondary eclipse, is $\sim a/R_\star \sim 9$\% (in the case that $a=5~\mathrm{AU}$ and $R_{\star}=100R_{\odot }$). 
%

>>>>

When stars less than $\sim$8~$M_\sun$ evolve off the main sequence, they evolve through the red-giant branch (RGB) and the asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude.
Jovian planets in orbit around such stars can migrate inward or outward due to the interplay between tidal torques and mass-loss process on the post-main sequence \citep{nordhaus_et_al2010,nordhaus+spiegel2013}.  During this time, such planets can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim 10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr. 
On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.

@@

\paragraph{Variability of stellar wind (a few months $\sim $)?}
If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time-variabililty of planetary radio emission.  Such variability might be expected to occur on timescales of several months to half-a-year as many M giants have semi-regular periodicities on the order of a few hundred days \citep{Kiss:1999aa}.

%
\paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
If the planetary orbit is close to the edge-on configuration, the radio emission disappears synchronously to the orbital period, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
The probability of the latter one, secondary eclipse, is $\sim a/R_\star \sim 9$\% (in the case that $a=5~\mathrm{AU}$ and $R_{\star}=100R_{\odot }$). 
%
